My Cool Title

### 2019-05-05 paper.tex
Added keywords, added openimage reference and real percentage for monitor/keyboard relatoonship

\begin{abstract}
  Cool abstract here
  \keywords{All the best keywords}
\end{abstract}

@@

\begin{equation}
  b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s)
\end{equation}

@@

$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages\todo{cite} dataset. 
For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e. UP) the object `keyboard' in 87\% \todo{get real percentage} of images containing both objects. 
The transition function for this case will look like

\begin{equation}
  \mathbf{T}(s, a, s') = \mathbf{T}(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.87
\end{equation}
An example of this relationship can be seen in the image in Fig.~\ref{fig:openimage}.

\begin{figure}
  \centering
  \includegraphics[width=0.5\columnwidth]{figures/desk_example.png}
  \caption{}\label{fig:openimage}
\end{figure}

>>>>

\begin{abstract}
  Cool abstract here
  \keywords{Active vision, vision impairment, object detection}
\end{abstract}

@@

\begin{equation}
  b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s), 
\end{equation}
where $\eta$ is a normalisation factor.

@@

$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages~\cite{openimages} dataset. 
For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e. UP) the object `keyboard' in 16\% of images containing both objects. 
The transition function for this case will look like

\begin{equation}
  \mathbf{T}(s, a, s') = \mathbf{T}(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
\end{equation}
An example of this relationship can be seen in the image in Fig.~\ref{fig:openimage}.

\begin{figure}
  \centering
  \includegraphics[width=0.5\columnwidth]{figures/desk_example.png}
  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects}\label{fig:openimage}
\end{figure}
